Twitter Sentiments Analysis
========================================================


```{r fig.width=7, fig.height=6}
#Load the required libraries
library("twitteR")
library("wordcloud")
library("tm")
library("ggplot2")
library("reshape2")
library("scales")

#Read tweets from text files 
ebayday1<-read.table(file="ebay_1.1.txt", skipNul = TRUE)
ebayday2<-read.table(file="ebay_2.txt", skipNul = TRUE)
ebayday3<-read.table(file="ebay_3.txt", skipNul = TRUE)
ebayday4<-read.table(file="ebay_4.txt", skipNul = TRUE)
ebayday5<-read.table(file="ebay_5.txt", skipNul = TRUE)

#Removing retweets 
tweetsday1<-ebayday1[-grep("RT @", ebayday1$text),]
tweetsday2<-ebayday2[-grep("RT @", ebayday2$text),]
tweetsday3<-ebayday3[-grep("RT @", ebayday3$text),]
tweetsday4<-ebayday4[-grep("RT @", ebayday4$text),]
tweetsday5<-ebayday5[-grep("RT @", ebayday5$text),]

tweetstextday1<-tweetsday1$text
tweetstextday2<-tweetsday2$text
tweetstextday3<-tweetsday3$text
tweetstextday4<-tweetsday4$text
tweetstextday5<-tweetsday5$text

#Load opinion Lexicon
pos <- scan("positive-words.txt",what="character",comment.char=";")
neg <- scan("negative-words.txt",what="character",comment.char=";")
```

Day 1
```{r fig.width=7, fig.height=6}
#Create the corpus
#this function belong to the tm package
tweetstextday1.corpus <- Corpus(VectorSource(tweetstextday1))

#Clean-up the corpus
#by converting it into lowercase, removing punctutation and
#removing the stopwords
tweetstextday1.corpus <- tm_map(tweetstextday1.corpus, tolower) 
tweetstextday1.corpus <- tm_map(tweetstextday1.corpus, removePunctuation)
tweetstextday1.corpus <- tm_map(tweetstextday1.corpus, function(x) removeWords(x,stopwords()))

# split the tweets in the corpus up into individual words
# lapply iterates over each element in the corpus and applies the strsplit function
# the splitting argument is the 3rd in the lapply function
# and is splitting on white space.
corpus.split.day1 <- lapply(tweetstextday1.corpus,strsplit,"\\s+")

# find matches for the individual words in the two lexicons
# lapply again, x takes on an element in the corpus
# at each iteration
matches1 <- lapply(corpus.split.day1,function(x) {
  match.pos.day1 <- match(x[[1]],pos)
  match.neg.day1 <- match(x[[1]],neg) 

  list(length(which(!is.na(match.pos.day1))),length(which(!is.na(match.neg.day1))))
})

# turn the matches into a matrix
# one column for positive, one for negative
match.matrix.day1 <- matrix(unlist(matches1),nrow=length(matches1),ncol=2,byrow=T)

# calculate a simple sentiment score by substracting
# positive count from negative count
simple.sentiment.day1 <- match.matrix.day1[,1] - match.matrix.day1[,2]

# histogram of sentiment
hist(simple.sentiment.day1)
```

```{r fig.width=7, fig.height=6}
#Create the corpus
#this function belong to the tm package
tweetstextday2.corpus <- Corpus(VectorSource(tweetstextday2))

#Clean-up the corpus
#by converting it into lowercase, removing punctutation and
#removing the stopwords
tweetstextday2.corpus <- tm_map(tweetstextday2.corpus, tolower) 
tweetstextday2.corpus <- tm_map(tweetstextday2.corpus, removePunctuation)
tweetstextday2.corpus <- tm_map(tweetstextday2.corpus, function(x) removeWords(x,stopwords()))

# split the tweets in the corpus up into individual words
# lapply iterates over each element in the corpus and applies the strsplit function
# the splitting argument is the 3rd in the lapply function
# and is splitting on white space.
corpus.split.day2 <- lapply(tweetstextday2.corpus,strsplit,"\\s+")

# find matches for the individual words in the two lexicons
# lapply again, x takes on an element in the corpus
# at each iteration
matches2 <- lapply(corpus.split.day2,function(x) {
  match.pos.day2 <- match(x[[1]],pos)
  match.neg.day2 <- match(x[[1]],neg) 

  list(length(which(!is.na(match.pos.day2))),length(which(!is.na(match.neg.day2))))
})

# turn the matches into a matrix
# one column for positive, one for negative
match.matrix.day2 <- matrix(unlist(matches2),nrow=length(matches2),ncol=2,byrow=T)

# calculate a simple sentiment score by substracting
# positive count from negative count
simple.sentiment.day2 <- match.matrix.day2[,1] - match.matrix.day2[,2]

# histogram of sentiment
hist(simple.sentiment.day2)
```

```{r fig.width=7, fig.height=6}
#Create the corpus
#this function belong to the tm package
tweetstextday3.corpus <- Corpus(VectorSource(tweetstextday3))

#Clean-up the corpus
#by converting it into lowercase, removing punctutation and
#removing the stopwords
tweetstextday3.corpus <- tm_map(tweetstextday3.corpus, tolower) 
tweetstextday3.corpus <- tm_map(tweetstextday3.corpus, removePunctuation)
tweetstextday3.corpus <- tm_map(tweetstextday3.corpus, function(x) removeWords(x,stopwords()))

# split the tweets in the corpus up into individual words
# lapply iterates over each element in the corpus and applies the strsplit function
# the splitting argument is the 3rd in the lapply function
# and is splitting on white space.
corpus.split.day3 <- lapply(tweetstextday3.corpus,strsplit,"\\s+")

# find matches for the individual words in the two lexicons
# lapply again, x takes on an element in the corpus
# at each iteration
matches3 <- lapply(corpus.split.day3,function(x) {
  match.pos.day3 <- match(x[[1]],pos)
  match.neg.day3 <- match(x[[1]],neg) 

  list(length(which(!is.na(match.pos.day3))),length(which(!is.na(match.neg.day3))))
})

# turn the matches into a matrix
# one column for positive, one for negative
match.matrix.day3 <- matrix(unlist(matches3),nrow=length(matches3),ncol=2,byrow=T)

# calculate a simple sentiment score by substracting
# positive count from negative count
simple.sentiment.day3 <- match.matrix.day3[,1] - match.matrix.day3[,2]

# histogram of sentiment
hist(simple.sentiment.day3)
```
Day 4
```{r fig.width=7, fig.height=6}
#Create the corpus
#this function belong to the tm package
tweetstextday4.corpus <- Corpus(VectorSource(tweetstextday4))

#Clean-up the corpus
#by converting it into lowercase, removing punctutation and
#removing the stopwords
tweetstextday4.corpus <- tm_map(tweetstextday4.corpus, tolower) 
tweetstextday4.corpus <- tm_map(tweetstextday4.corpus, removePunctuation)
tweetstextday4.corpus <- tm_map(tweetstextday4.corpus, function(x) removeWords(x,stopwords()))

# split the tweets in the corpus up into individual words
# lapply iterates over each element in the corpus and applies the strsplit function
# the splitting argument is the 3rd in the lapply function
# and is splitting on white space.
corpus.split.day4 <- lapply(tweetstextday4.corpus,strsplit,"\\s+")

# find matches for the individual words in the two lexicons
# lapply again, x takes on an element in the corpus
# at each iteration
matches4 <- lapply(corpus.split.day4,function(x) {
  match.pos.day4 <- match(x[[1]],pos)
  match.neg.day4 <- match(x[[1]],neg) 

  list(length(which(!is.na(match.pos.day4))),length(which(!is.na(match.neg.day4))))
})

# turn the matches into a matrix
# one column for positive, one for negative
match.matrix.day4 <- matrix(unlist(matches4),nrow=length(matches4),ncol=2,byrow=T)

# calculate a simple sentiment score by substracting
# positive count from negative count
simple.sentiment.day4 <- match.matrix.day4[,1] - match.matrix.day4[,2]

# histogram of sentiment
hist(simple.sentiment.day4)
```

```{r fig.width=7, fig.height=6}
#Create the corpus
#this function belong to the tm package
tweetstextday5.corpus <- Corpus(VectorSource(tweetstextday5))

#Clean-up the corpus
#by converting it into lowercase, removing punctutation and
#removing the stopwords
tweetstextday5.corpus <- tm_map(tweetstextday5.corpus, tolower) 
tweetstextday5.corpus <- tm_map(tweetstextday5.corpus, removePunctuation)
tweetstextday5.corpus <- tm_map(tweetstextday5.corpus, function(x) removeWords(x,stopwords()))

# split the tweets in the corpus up into individual words
# lapply iterates over each element in the corpus and applies the strsplit function
# the splitting argument is the 3rd in the lapply function
# and is splitting on white space.
corpus.split.day5 <- lapply(tweetstextday5.corpus,strsplit,"\\s+")

# find matches for the individual words in the two lexicons
# lapply again, x takes on an element in the corpus
# at each iteration
matches5 <- lapply(corpus.split.day5,function(x) {
  match.pos.day5 <- match(x[[1]],pos)
  match.neg.day5 <- match(x[[1]],neg) 

  list(length(which(!is.na(match.pos.day5))),length(which(!is.na(match.neg.day5))))
})

# turn the matches into a matrix
# one column for positive, one for negative
match.matrix.day5 <- matrix(unlist(matches5),nrow=length(matches5),ncol=2,byrow=T)

# calculate a simple sentiment score by substracting
# positive count from negative count
simple.sentiment.day5 <- match.matrix.day5[,1] - match.matrix.day5[,2]

# histogram of sentiment
hist(simple.sentiment.day5)
```


```{r fig.width=7, fig.height=6}
#Calculate the sum of the sentiments for each day
sentiment.day1<-sum(simple.sentiment.day1)
sentiment.day2<-sum(simple.sentiment.day2)
sentiment.day3<-sum(simple.sentiment.day3)
sentiment.day4<-sum(simple.sentiment.day4)
sentiment.day5<-sum(simple.sentiment.day5)

#Setting levels for the Sentiment values
#Level 1 means a positive sentiment
#and level -1 means a negative sentiment
sentimentlevel.day1<-ifelse(sentiment.day1>0, 1, -1)
sentimentlevel.day2<-ifelse(sentiment.day2>0, 1, -1)
sentimentlevel.day3<-ifelse(sentiment.day3>0, 1, -1)
sentimentlevel.day4<-ifelse(sentiment.day4>0, 1, -1)
sentimentlevel.day5<-ifelse(sentiment.day5>0, 1, -1)

#Create a data frame of the sentiment levels obtained
Sentiment<-c(sentimentlevel.day1,sentimentlevel.day2,sentimentlevel.day3,sentimentlevel.day4,sentimentlevel.day5)

#Stock levels are set based on the stock available from the market
#level 1 means that the company closed with a gain on the stock for the day
#and level -1 means that the company closed with a loss
Stock<-c(-1, 1, -1, -1, 1)

#Create a data frame of the dates used
Day<-c(as.Date("2014-12-03"),as.Date("2014-12-04"),as.Date("2014-12-05"),
        as.Date("2014-12-08"), as.Date("2014-12-09"))

#Create the final data frame
df.final<-data.frame(Day,Sentiment, Stock)

#Melt the data frame to convert it into a long format for plotting 
molten.df.final<-melt(df.final, id.vars="Day")

#Plotting the stock market and sentiment level comparison
ggplot(molten.df.final, aes(Day, value, fill = variable)) +
  geom_bar(stat="identity", position=position_dodge()) +
  ylab("Sentiment/Stock Value") +
  scale_y_continuous(limits = c(-1, 1))+
  scale_x_date(labels = date_format("%b-%d")) +
  scale_fill_discrete(name="Legend",
                         breaks=c("Sentiment", "Stock"),
                         labels=c("Sentiment Value", "Stock Price"))
```


Summary
-------
Assignment was to gather the tweets for eBay for 5 days, to see if the sentiments expressed in twitters have effect onstock prices.In this to calculated sentiment value for each day a difference between the number of positive and negative words from the tweets were taken. Also, retweets were removed. For ebay analysis I found that the sentiments were always positive for these 5 days. But the stock values had both positive and negative changes. 

Therefore,  positive sentiments from twitter cannot predict the stock price rise. There are many other factors which can effect the stock market.